% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[review]{EACL2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}


% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Difficulties of Detecting Hate Speech in Culturally Embedded Language: \\
A Case Study of White Supremacist Literature}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\begin{document}
\maketitle
\begin{abstract}
This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style file for EACL 2023.
The document itself conforms to its own specifications, and is, therefore, an example of what your manuscript should look like.
These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

\section{Introduction} \label{sec:intro}

The field of NLP has made great strides in recent years from representation learning (e.g., Word2vec \cite{mikolov2013distributed}) 
to fine-tuning pre-trained language models (e.g., BERT \cite{devlin2018bert}) \cite{naseem2021comprehensive} to achieve state-of-the-art performance on a wide range of NLP tasks.
This development of NLP has been accompanied by various benchmarks and datasets, which have been used to evaluate the performance of NLP models \cite{park2022raison}.
The field of hate speech detection has also benefited from the development of NLP, with various datasets and benchmarks. Despite varied definitions of hate speech \cite{fortuna2020toxic}, 
the field has made progress  thanks to the availability of text data from Wikipedia Talk Pages \cite{wulczyn2017ex}, 
Twitter \cite{waseem2016hateful}, and website forum like Stormfront \cite{de2018hate} where White supremacists congregate. 
However, there has been little work on the detection of hate speech in literature in general. This might be in part due to 
the sparsity of White supremacist literature in 21st century America. However, in the 20th century, White supremacist
literature was published and formed a unique genre called \textit{``Anti-Tom''} literature, as opposed to 
\textit{``Uncle Tom's Cabin''} by Harriet Beecher Stowe. \textit{``Anti-Tom''} genre shares similar idea of 
``The Lost Cause of the Confederacy''  which embodies
the tenets that Southern men fought for a just cause (e.g., rights of property, 
and self-determination) \cite{pollard1866lost} and the defeat of the Confederacy has led to the
destruction of the values of the South \cite{foster1987ghosts,gulley1993women}. 
In opposition to the \textit{``Uncle Tom's Cabin''}, where slavery is depicted as an evil institution,
depraving slaves of their humanity, \textit{``Anti-Tom''} literature is characterized by
provoking positive image of slavery with benevolent masters and happy slaves \cite{petertempletonAntiTomLiteratureSpotlight2022}.
This image is well-illustrated in the novel and the film, \textit{``Gone with the Wind''} by Margaret Mitchell.
Among the writers of White supremacist literature, Thomas Dixon Jr. is one of the most prominent writers. 
His trilogy, \textit{``The Leopard's Spots''}, \textit{``The Clansman''}, and \textit{``The Traitor''}
created a fictional character in the Ku Klux Klan and his passionate Black-phobia
was framed as a heroic and romantic quality. Dixon's book attracted a large audience. The first edition of 
\textit{``The Leopard's Spots''} comprising 15,000 copies was exhausted on publication \cite{bloomfield1964dixon}.

In this study, we use Dixon's trilogy as a case study of applying hate speech detection datasets made in the 21st century 
and examining the text the large language model generates with hateful text written in the 20th century.
To the best of our knowledge, this study attempts to analyze ``Anti-Tom'' or White supremacy genre literature 
with NLP for the first time.
The contribution of this study is two-fold. (1) This study provides a benchmark result by comparing the performance of classifiers from traditional feature-based classifiers to
pre-trained language model classifiers to examine which of NLP model works the best in detecting hateful language written in the 20th century.
(2) This study uses the hateful text from the literature as a prompt for generative AI, Llama 2 \cite{touvron2023llama2} and examined the generated
text by Llama 2.

We found (1) XXX and (2) YYY.

\section{Related Works} \label{sec:related_works}

\subsection{Application of NLP to Historical Texts} \label{sec:application_nlp}
Applying NLP to the historical text is not a new idea. 
\citet{pedrazzini2022machines} used a diachronic word embedding
to trace the semantic change of the word associated with Industrial
Revolution and presented how the meaning of the word shifted 
in digitized 19th century British newspapers. 
\citet{soni2021abolitionist} also used the abolitionist newspapers from
the 19th century to trace semantic changes of the word by using 
diachronic word embeddings similar to \citeauthor{pedrazzini2022machines}.
Another research group took a large scale digitized historical newspapers
and used NLP technique to detect the text reprints in the historical newspapers \cite{smith2013infectious}

While aforementioned studies used historical newspapers as a primary corpus for the analysis,
there also have been studies on applying NLP to historical literature.
\citet{parulian2022uncovering} studied word features by comparing
Bag-of-Words and full-text embeddings and classified 
Black Fantastic genre with feature-based classifiers.
Another study using Project Gutenberg corpus compared 
deep learning models and traditional feature-based method for 
genre classification \cite{worsham2018genre}.

However, there has been a gap of understanding the White supremacist literature, 
especially the genre called \textit{``Anti-Tom''} and there has been no work on applying
datasets created in the 21st century to the literature written in the 20th century. 
This study attempts to fill this gap by applying the datasets created in the 21st century
and examine the performance of the classifiers. The advancement of hate speech detection
in NLP is presented in the following section \ref{sec:hate_speech_detection}.

\subsection{Hate Speech Detection} \label{sec:hate_speech_detection}
The rise of social media has made easy-to-access text data available for NLP research.
The online communication space play a role as a space for sharing
ideas and opinions \cite{ocal2021reasoning}, but its anonymity and lack of accountability 
have led to the proliferation of hate speech \cite{fortuna2020toxic}.
Social media platform like Twitter and Reddit has attracted researchers to 
collect, annotate, and publish datasets for hate speech detection \cite{waseem2016hateful,kennedy2017technology}. Among 
many other datasets, \citet{wulczyn2017ex} collected personal attack
comments from Wikipedia discussion pages and annotated them with crowd-sourcing. 
Another popular hate speech dataset is from Twitter with three 
categories of racism, sexism, and neither \cite{waseem2016hateful}. 

While these datasets have collected text data from online space that is not
necessarily a communication space for White supremacists, White supremacist
forum like Stormfront and Gab have also been used to collect text data 
for hate speech detection \cite{de2018hate} and study echo chambers \cite{zannettou2018gab}.
The availability of these datasets also have led to create a service
for online content moderation \cite{rieder2021fabrics}, called Perspective API.
Perspective API \footnote{\url{https://www.perspectiveapi.com/}} is a service 
hosted by Google that provides a degree of toxicity of the text input. 
Many research on incivil behavior in online space have used Perspective API 
to quantify the toxicity of the text \cite{rajadesingan2021political,chong2022understanding}.

% \subsection{Generative AI and Impact} \label{sec:generative_ai_impact}
% The generative AI has received a lot of attention in recent years.
% The good performance in professional fields like bar exam \cite{katz2023gpt}
% and writing \cite{elkins2020can} surprised the public and researchers in NLP.
% However, the immeasurable size of the model and the lack of understanding of the model 
% have raised concerns about the potential harm of the generative AI \cite{bender2021dangers}.
% As \citet{mcguffie2020radicalization} reports, large language models (LLMs) 
% like GPT-3 \cite{brown2020language} can generate text that integrates 
% niche knowledge with radical ideologies and bias (e.g., QAnon, Anti-Semitic, and mass shooting).
% So-called ``Garbage-in and garbage-out'' could explain
% the amplification of the negative, stereotypical, and derogatory language \cite{dinan2021anticipating}.
% We witnessed the harm of the LLMs in the case of Tay, a chatbot developed by Microsoft
% that generated racist, sexist, and anti-Semitic language \cite{wolf2017we}.
% The impact of the LLMs could be worse if humans interact with the LLMs more often
% as the access boundary of generative AI is lowered \cite{park2022raison}.
% One study experimented that when participants write an argumentative essay with
% the help of AI system, they reported that the way of thinking
% is changed and they are more likely to agree with what AI system suggests 
% \cite{fyfe2022cheat}. Therefore, a careful consideration of the quality of dataset is needed 
% to prevent the amplification of negative language \cite{gunasekar2023textbooks}.

\subsection{Problems of Hate Speech Datasets} \label{sec:problems_hate_speech_datasets}

Despite advances in NLP have made a great progress in hate speech detection,
there are still problems in hate speech detection. 
\citet{vidgen2019challenges} summarized the challenges of hate speech detection
in three categories: (1) the lack of a clear agreement on the type of hate speech (e.g., 
individual-directed abuse, identity-directed abuse, and concept-directed abuse),
(2) the lack of a clear definition of terminology in use (e.g., the intention of the speaker,
the effect of abuse, and the sensibilities of the audience) and (3) the lack of a clear
context of the text. \citeauthor{vidgen2019challenges} brings the example of the term
\textit{n-word} has an almost opposite meaning if spoken by a White compared to a Black person.

In similar vein, \citet{sap2019risk} empirically showed that hate speech detection
models are biased against African American English (AAE). 
They found that the \textit{n-word} is more associated with toxicity in Perspective API
and the argued that the speaker's identity becomes a factor in determining the toxicity of the text.
To mitigate such racial bias, one study experimented with syntactic feature of AAE
and tested if correcting the AAE grammar to Standard American English (SAE) 
could help reduced flagging AAE as toxic \cite{harris2022exploring}.
Another study Neural classifiers are more known to be over-sensitive to group identifiers like
``Muslim'' and ``Black'' \cite{kennedy2020context}.


\section{Methodology} \label{sec:methodology}

\subsection{Thomas Dixon Jr's Trilogy} \label{sec:thomas_dixon}
The full text of \textit{``The Leopard's Spots''}, \textit{``The Clansman''}, and \textit{``The Traitor''} 
are available in HathiTrust Digital Library \footnote{\url{https://babel.hathitrust.org}}. 
The text was cleaned by removing the HathiTrust terms of use and copyright 
information at the beginning and the end of the text.
Once the text is cleaned, we used BookNLP \cite{bamman2014bayesian} 
to extract the speech of the characters in the novel.
The extracted quotes are used as a training data for the hate speech detection model.

\subsection{Human Annotation} \label{sec:human_annotation}

Two authors of this study annotated the quotes extracted from the novels.
The annotation followed the definition of datasets used in this study (see section \ref{sec:datasets}).

Although the first African American immigrants did not prefer \textit{n-word} 
to refer to themselves \cite{bennett1969s}, the \textit{n-word} remained
the standard term for African Americans until the 20th century.
African American leaders like Booker T. Washington and W.E.B. Du Bois used the word 
\textit{n-word} in their speeches and writings \cite{smith1992changing}.
As the \textit{n-word} becomes a slur when speakers intentionally
use the word to degrade African Americans \cite{kennedy1999can}, 
\textit{n-word} written in the 20th century literature may not
necessarily be a derogatory term.
Culturally accepted terms change over time. Therefore, we adopted the language culture 
of the 20th century and regarded the \textit{n-word},
\textit{colored people} and/or \textit{black} not as a derogatory term in annotation.
When the \textit{n-word} is used without any word that conveys derogatory meaning,
we annotated non-hateful. That being said, whether the quote is hateful or not
was determined by the context of the quote, not by the existence of the \textit{n-word}.
Instead, we annotated the quotes that convey White supremacist ideology such as
upholding slavery and Black inferiority (such as opposing Black suffrage) as hateful.
However, general statements of restoring Confederacy and Southern pride were
not annotated as hateful.

\subsection{Datasets for Classification} \label{sec:datasets}
The hate speech dataset comprises sexism or anti-semitism or, anti-Asian could be irrelevant
to the White supremacist literature. Therefore, we chose the dataset that is situated in the
context of the White supremacist ideology and targeted to African Americans.
The first dataset 

  

\subsection{Generative AI and Measuring Toxicity} \label{sec:generative_ai}

\citet{touvron2023llama} released Llama with publicly available datasets with
open-source code, compared to GPT-3 \cite{brown2020language} which is a proprietary model.
We used Llama 2 inference model with 13B parameters implemented in C++ \footnote{\url{https://github.com/ggerganov/llama.cpp}}.
In the fine-tuning process, we used \textit{n=64} to predict 64 tokens to predict when generating text (default=128)
and \textit{n=1.5} to pose a penalty on the repetition of the tokens (default=1.1). The rest of 
the parameters are set to default. We used the speech of the characters in the novel as a prompt
for the Llama 2. The generated text is evaluated with Perspective API. 



\subsection{Experiments} \label{sec:experiments}

Train: 20C White supremacy literature VS Test: 21C century dataset 
Train: 21C hate speech dataset VS Test: 20C White supremacy literature
Llama 2

\section{Results} \label{sec:results}

\section{Discussion}
Error analysis reveals that the 21C hate speech dataset is overfitted 
to the word ``negro'' although the word ``negro'' may not
necessarily be a derogatory word to refer to African Americans in the 20C. 

Social media affordances like hashtags and emojis are not present in the 20C literature. 



% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is a section in the appendix. Error analysis?

\end{document}
